A fast unified model for parsing and sentence understanding

### 2016-03-17 writing/hard_stack_paper/paper.tex
Last few technical fixes.

\input{batching_fig.tex}
\input{../model1_fig.tex}
\todo{[SB,JG,AR,RG] Trim mercilessly whenever you see anything redundant.}

@@

In this section, we compare the test time speed of our SPINN-PI-NT with an equivalent TreeRNN implemented in the conventional fashion. While the full models evaluated above are implemented and trained using Theano \todo{[SB] Cite Theano.}, which is reasonably efficient but not perfect for our model, we wish to compare well-optimized implementations of both models here. To do this, we reimplement the feedforward of SPINN-PI-NT in C++/CUDA, and we compare that implementation with a CPU-based C++/Eigen TreeRNN implementation from \citet{irsoy2014deep}, which we modified to perform exactly the same computations as our model.\footnote{The original code for Irsoy \& Cardie's model is available at \url{https://github.com/oir/deep-recursive}. We plan to release our modified code at publication time, alongside the Theano source code for the full SPINN.} TreeRNNs like this can only operate on a single example at a time and are thus poorly suited for GPU computation.\footnote{We chose to reimplement and evaluate only the thin-stack feedforward (not training/backpropagation) in C++/CUDA, as feedforward/inference speed is the relevant performance metric for most practical applications.}

Each model is restricted to run on sentences of 30 tokens or fewer (for SPINN, this means we iterate over a sequence of 59 transitions). We fix the model dimension and the word embedding dimension at 300. We run the CPU performance test on a 2.20-GHz Intel Xeon processor with hyperthreading enabled. Our GPU model is implemented in C++ and CUDA, and will be released with the rest of our code. We test it on a NVIDIA Titan X GPU. \todo{[SB, JG] Is Titan X sufficiently unambiguous?}

@@

\todo{[SB] Track down mystery spaces.}

\begin{table*}[t]\small
\begin{center}
\begin{tabular}{lrlrrrr}
\toprule
Param.     & Range & Strategy        & RNN       & SPINN-PI-NT   & SPINN-PI  & SPINN \\
\midrule 
Initial LR & 2e-4--2e-2 & \textsc{log} & 5e-3  & 3e-4 & 7e-3  & SPINN\\
L2 regularization $\lambda$ & 8e-7--3e-5   & \textsc{log} & 4e-6  & 3e-6   & 2e-5  & SPINN\\
Transition cost $\alpha$  & 0.5--4.0 & \textsc{lin} & N/A & N/A & N/A  & SPINN\\
Embedding transformation dropout keep rate & 80\%--95\% & \textsc{lin} & N/A & 83\% & 92\%  & SPINN\\
Classifier MLP dropout keep rate & 80\%--95\% & \textsc{lin} & 94\%  & 94\%   & 93\%  & SPINN\\
Tracking LSTM size $D_t$ & 24--128 & \textsc{log} & N/A & N/A & 61  & SPINN\\
Classifier MLP layers & 1--3 & \textsc{lin} & 2 & 2 & 2 & SPINN\\
\bottomrule
\end{tabular}
\end{center}

\caption{
\label{tab:hyperparams}
Hyperparameter ranges and values. \ii{Range} shows the hyperparameter ranges explored during random search. \ii{Strategy} indicates whether sampling from the range was uniform, or log--uniform. \result{[SB] Full model hyperparams.}
}
\end{table*}

>>>>

\input{batching_fig.tex}
\input{../model1_fig.tex}

@@

In this section, we compare the test time speed of our SPINN-PI-NT with an equivalent TreeRNN implemented in the conventional fashion. While the full models evaluated above are implemented and trained using Theano \citep{bergstra+al:2010-scipy,Bastien-Theano-2012}, which is reasonably efficient but not perfect for our model, we wish to compare well-optimized implementations of both models here. To do this, we reimplement the feedforward of SPINN-PI-NT in C++/CUDA, and we compare that implementation with a CPU-based C++/Eigen TreeRNN implementation from \citet{irsoy2014deep}, which we modified to perform exactly the same computations as our model.\footnote{The original code for Irsoy \& Cardie's model is available at \url{https://github.com/oir/deep-recursive}. We plan to release our modified code at publication time, alongside the Theano source code for the full SPINN.} TreeRNNs like this can only operate on a single example at a time and are thus poorly suited for GPU computation.\footnote{We chose to reimplement and evaluate only the thin-stack feedforward (not training/backpropagation) in C++/CUDA, as feedforward/inference speed is the relevant performance metric for most practical applications.}

Each model is restricted to run on sentences of 30 tokens or fewer (for SPINN, this means we iterate over a sequence of 59 transitions). We fix the model dimension and the word embedding dimension at 300. We run the CPU performance test on a 2.20-GHz Intel Xeon processor with hyperthreading enabled. Our GPU model is implemented in C++ and CUDA, and will be released with the rest of our code. We test it on a NVIDIA Titan X GPU.

@@

\begin{table*}[t]\small
\begin{center}
\begin{tabular}{lrlrrrr}
\toprule
Param.     & Range & Strategy        & RNN       & SPINN-PI-NT   & SPINN-PI  & SPINN \\
\midrule 
Initial LR & 2e-4--2e-2 & \textsc{log} & 5e-3  & 3e-4 & 7e-3  & 2e-3\\
L2 regularization $\lambda$ & 8e-7--3e-5   & \textsc{log} & 4e-6  & 3e-6   & 2e-5  & 3e-5\\
Transition cost $\alpha$  & 0.5--4.0 & \textsc{lin} & --- & --- & ---  & 3.9    \\
Embedding transformation dropout keep rate & 80--95\% & \textsc{lin} & --- & 83\% & 92\%  & 86\%\\
Classifier MLP dropout keep rate & 80--95\% & \textsc{lin} & 94\%  & 94\%   & 93\%  & 94\%\\
Tracking LSTM size $D_t$ & 24--128 & \textsc{log} & --- & --- & 61  & 79\\
Classifier MLP layers & 1--3 & \textsc{lin} & 2 & 2 & 2 & 1\\
\bottomrule
\end{tabular}
\end{center}

\caption{
\label{tab:hyperparams}
Hyperparameter ranges and values. \ii{Range} shows the hyperparameter ranges explored during random search. \ii{Strategy} indicates whether sampling from the range was uniform, or log--uniform.
}
\end{table*}
